### 2018-05-23 VV570/HW1/assignment.tex
add ex5.1

\begin{enumerate}
\item $y=\frac{1}{x}$ is continuous over $(0, +\infty)$, but not uniform continuous.
      \begin{proof}
      	Let $x_1 = \frac{1}{n+1}$,  $x_2 = \frac{1}{n}$. 
      	Then $\lim\limits_{n \rightarrow +\infty} x_2-x_1 = \frac{1}{n(n+1)} = 0 $.
      	But $\lim\limits_{n \rightarrow +\infty} y_2- y_1 = -1 \neq 0 $.
      	Thus it is not uniform continuous.
      \end{proof}
\item $y=\sqrt{x}$ is uniform continuous over $(0, +\infty)$ but not Lipschitz continuous.
	  \begin{proof}
	  	As $y\prime = \frac{1}{2\sqrt{x}}$, 
	  	the slope tends towards infty when $x$ approaches 0, 
	  	thus it is not Lipschitz continuous.  
	  \end{proof}
\end{enumerate}

@@

>>>>

\begin{enumerate}
\item $y=\frac{1}{x}$ is continuous over $(0, +\infty)$, but not uniform continuous.
      \begin{proof}
      	Let $x_1 = \frac{1}{n+1}$,  $x_2 = \frac{1}{n}$. 
      	Then $\lim\limits_{n \rightarrow +\infty} \vert x_2-x_1 \vert = \frac{1}{n(n+1)} = 0 $.
      	But $\lim\limits_{n \rightarrow +\infty} \vert y_2- y_1 \vert = 1 \neq 0 $.
      	Thus it is not uniform continuous.
      \end{proof}
\item $y=\sqrt{x}$ is uniform continuous over $(0, +\infty)$ but not Lipschitz continuous.
	  \begin{proof}
	  	As $y\prime = \frac{1}{2\sqrt{x}}$, 
	  	the slope tends towards infty when $x$ approaches 0, 
	  	thus it is not Lipschitz continuous.  
	  \end{proof}
\end{enumerate}

@@

%----------------------------------------------------------------------------------------
%	PROBLEM 5
%----------------------------------------------------------------------------------------

\section{Linear Algebra}

\begin{enumerate}
	\item
		\begin{proof}
			Suppose $\{u_1, u_2, ... , u_m \}$ forms the basis of Ker($f$), and it can be extended to form the basis of $V_1$, which is denoted as $\{u_1, u_2, ... , u_m, v_1, v_2, ... , v_n \}$. It's clear that the dimension of Ker($f$) is $m$ and the dimension of $V_1$ is $m+n$. So, it is left to prove that the dimension of $V_2$ is $n$.

			The dimension of $V_2$ is $n$ means $\{f(v_1), f(v_2), ... , f(v_n)\}$ forms a basis of $V_2$. To see that, let $w$ be an arbitary vector in $V_1$, thus, there exist unique scalars $a_i$, $b_j$ such that 
			\begin{equation}
				w = a_1 u_1 + a_2 u_2 + ... + a_m u_m + b_1 v_1 + b_2 v_2 + ... + b_n v_n
			\end{equation}

			The image of $w$ under mapping $f$ is given as below.
			\begin{equation}
				\begin{aligned}
					f(w) & = \sum_{i=1}^{m}a_i f(u_i) + \sum_{j=1}^{m}b_j f(v_j) \\
						 & = \sum_{j=1}^{m}b_j f(v_j)  \ \ \ \  \text{As $f(u_i) = 0$}
				\end{aligned}
			\end{equation}

			Thus $\{f(v_1), f(v_2), ... , f(v_n)\}$ spans $V_2$. It is left to show that they are linearly independent, which means there's no redundancy in the list.

			Given coefficents $c_i$ such that
			\begin{equation}
				c_1 f(v_1) + c_2 f(v_2) + ... + c_n f(v_n) = 0 \label{cdis}
			\end{equation}

			Since $f$ is a linear mapping, (\ref{cdis}) can be grouped as below.
			\begin{equation}
				f(c_1 v_1 + c_2 v_2 + ... + c_n v_n) = 0
			\end{equation}

			Thus $c_1 v_1 + c_2 v_2 + ... + c_n v_n \in Ker(f)$. As $\{u_1, u_2, ... , u_m \}$ forms the basis of Ker($f$), there exists coefficients $d_i$ such that
			\begin{equation}
				c_1 v_1 + c_2 v_2 + ... + c_n v_n = d_1 u_1 + d_2 u_2 + ... + d_m u_m \label{diff}
			\end{equation}

			Since $\{u_1, u_2, ... , u_m, v_1, v_2, ... , v_n \}$ forms the basis of $V_1$, all the coefficients in (\ref{diff}) should be 0. Thus, (\ref{cdis}) is valid if and only if all the coefficents $c_i$ is 0, which implies that $\{f(v_1), f(v_2), ... , f(v_n)\}$ are linearly independent.

			Thus, $\{f(v_1), f(v_2), ... , f(v_n)\}$ forms the basis of $V_2$, and the dimension of $V_2$ is therefore $n$. The rank-nullity theorem written as below is proved.
			\begin{equation}
				dim(V_1) = dim(ker(f)) + dim(V_2)
			\end{equation}
		\end{proof}
	\item
		\begin{proof}

		\end{proof}
	\item
		\begin{proof}
